# BKPC R package. 

To install use  


```{r, eval=FALSE}
devtools::install_git("https://gitlab.com/domijank/BKPC.git")
```

Bayesian kernel projection classifier (BKPC) is a nonlinear multicategory classifier which performs the classification of the projections of the data to the principal axes of the feature space. A Gibbs sampler is implemented to find the posterior distributions of the parameters. 

The main function is bkpc. 

The data can be passed to the bkpc function as:

- a matrix of features,

- a kernel matrix of either:



* class 'kern' (a Gaussian kernel computed using the gaussKern{BKPC} function) or 
* class 'kernelMatrix' from library kernlab. This allows for a wider selection of inbuilt kernel generating functions as well as user defined functions.

The package contains a microarray dataset and a function to extract the marginal relevance of each feature for classification.


For an example of running bkpc see below:
```{r, eval=FALSE}
set.seed(-88106935)
library(BKPC)
data(microarray)

# consider only four tumour classes (NOTE: "NORM" is not a class of tumour)
y <- microarray[, 2309]
train <- as.matrix(microarray[y != "NORM", -2309])
wtr <- factor(microarray[y != "NORM", 2309], levels = c("BL" ,  "EWS" , "NB" ,"RMS" ))

n.kpc <- 6
n.class <- length(levels(wtr)) - 1

K <- gaussKern(train)$K

# supply starting values for the parameters
# use Gaussian kernel as input

result <- bkpc(K, y = wtr, n.iter = 1000,  thin = 10, n.kpc = n.kpc,  
initSigmasq = 0.001, initBeta = matrix(10, n.kpc *n.class, 1), 
initTau =matrix(10, n.kpc * n.class, 1), intercept = FALSE, rotate = TRUE)

# predict

out <- predict(result, n.burnin = 10) 

table(out$class, as.numeric(wtr))

# plot the data projection on the kernel principal components

pairs(result$kPCA$KPCs[, 1 : n.kpc], col = as.numeric(wtr), 
main =  paste("symbol = predicted class", "\n", "color = true class" ), 
pch = out$class, upper.panel = NULL)
par(xpd=TRUE)
legend('topright', levels(wtr), pch = unique(out$class), 
text.col = as.numeric(unique(wtr)), bty = "n")

```


For an example of feature selection using marginal relevance see:
```{r, eval=FALSE}

data(microarray)

profiles <- as.matrix(microarray[, -2309])
tumourType <-  microarray[, 2309]
 
margRelv <- marginalRelevance(profiles, tumourType)

# plot 30 gene profiles with highest marginal relevance score
plot(margRelv, type = "parallelcoord", n.feat = 50, col = tumourType )
```




